%-------------------------
% Resume in Latex
% Author : Chandana Shastri
% Based off of: https://github.com/chandanas03/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Chandana Shastri} \\ \vspace{1pt}
    \href{mailto:chandanasthastri12@gmail.com}{\underline{chandanasthastri12@gmail.com}} $|$ 
    \href{https://chandanas03.github.io/Portfolio/}{\underline{http://chandana.social}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of Mumbai}{Navi Mumbai, Maharashtra}
      {B.E. in Artificial Intelligence \& Machine Learning, Honours in Data Science}{Aug. 2021 -- June 2025}

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {LeadGenius}{Berkeley, California [remote]}
      {Data Researcher}{Sep. 2021 -- Dec. 2021}
      \resumeItemListStart
        \resumeItem{Conducted data research for marketing, lead management, and data solutions}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------INTERNSHIPS-----------
\section{Internships}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PODS Technology Solutions}{Navi Mumbai, Maharashtra}
      {Machine Learning Intern}{Jan. 2025 -- Feb. 2025}
      \resumeItemListStart
        \resumeItem{Developed a text-to-image generation model using GANs and VAEs to transform natural language into visuals}
      \resumeItemListEnd
    \resumeSubheading
      {IEEE Bombay Section}{Mumbai, Maharashtra[remote]}
      {Jr. Full Stack Developer}{Sep. 2023 -- Nov. 2023}
      \resumeItemListStart
        \resumeItem{Collaborated on a full-stack web application using Svelte and SvelteKit}
      \resumeItemListEnd
    \resumeSubheading
      {Cyberi Pvt. Ltd.}{Mumbai, Maharashtra}
      {Machine Learning Intern}{Jun. 2023 -- Aug. 2023}
      \resumeItemListStart
        \resumeItem{Built the backend for an AI-powered search system for cybersecurity data}
      \resumeItemListEnd
    \resumeSubheading
      {PHN Technology Pvt. Ltd.}{Pune, Maharashtra, India [remote]}
      {Machine Learning \& Data Science Intern}{Apr. 2023 -- Jun. 2023}
      \resumeItemListStart
        \resumeItem{Gained hands-on experience in ML and DS using Python, sklearn, numpy, pandas, and matplotlib}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Auto Vision: AI-Powered Vehicle Damage Assessment} $|$ \emph{Python, ML, DL}}{Jan. 2024 -- May 2024}
      \resumeItemListStart
        \resumeItem{Built a system that can accurately classify various types of car damage. Incorporated OCR capabilities for license
plate verification using the easyocr and cv2 libraries.Fine-tuned the model to enhance its accuracy. Hosted the
project on Hugging Face Spaces for easy access and used Gradio for the interface
\href{https://www.linkedin.com/posts/chandanashastri_autovision-ai-machinelearning-activity-7190037479909969921-WMZe?utm_source=share&utm_medium=member_desktop&rcm=ACoAADK9cGQBBQ2ytaQ6riFqnJbrcOA1OnfGoc0}{\textbf{AutoVision}}}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Cloud Computing} $|$ \emph{S3, IAM, EC2, RDS, AWS }}{Mar. 2024 -- May 2024}
      \resumeItemListStart
        \resumeItem{We utilized Amazon S3 for storing our website code, ensuring seamless access and scalability. Implemented a secure
login/signup page using AWS IAM (Identity and Access Management) to ensure robust security and compliance
with SECaaS standards. Integrated a chatbot feature providing real-time interaction and engagement. Leveraged
DBaaS (Database as a Service) for newsletter signup, streamlining user data management
\href{https://www.linkedin.com/posts/chandanashastri_miniabrproject-s3-iam-activity-7192055727035748352-mi7b?utm_source=share&utm_medium=member_desktop&rcm=ACoAADK9cGQBBQ2ytaQ6riFqnJbrcOA1OnfGoc0}{\textbf{AWS Cloud}}}
    \resumeItemListEnd  

   \resumeProjectHeading
      {\textbf{Gizzz 101} $|$ \emph{Hugging Face API, Node.js, Replit }}{Mar. 2024 -- May 2024}
      \resumeItemListStart
        \resumeItem{full-stack AI text summarizer app \href{https://www.linkedin.com/posts/activity-7122321184368594945-2rVt?utm_source=share&utm_medium=member_desktop&rcm=ACoAADK9cGQBBQ2ytaQ6riFqnJbrcOA1OnfGoc0}{\textbf{Gizzz 101}}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd

%-----------POSITIONS OF RESPONSIBILITY-----------
\section{Positions of Responsibility}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technical Head}{SIES Graduate School of Technology}
      {IEEE SIESGST Team}{2023 -- 2024}
      \resumeItemListStart
        \resumeItem{Developed websites and hardware projects for STEM workshops and \textbf{Techopedia}  event}
        \resumeItem{Guided technical volunteers and Organized technical events}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
    \resumeSubheading
      {AI/ML Department Coordinator}{SIES Graduate School of Technology}
      {Training and Placement Cell}{2023 -- 2024}
      \resumeItemListStart
        \resumeItem{Co-ordinated for placement drives}
        \resumeItem{Hosted multiple events in T\&P cell}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
      \resumeSubHeadingListStart
    \resumeSubheading
      {Media Volunteer}{SIES Graduate School of Technology}
      {Media Team}{2022 -- 2023}
      \resumeItemListStart
        \resumeItem{Photography, Cinematography}
        \resumeItem{Adobe Lightroom editing}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, R, PHP} \\
     \textbf{Web Technologies}{:HTML, CSS, Javascript} \\
     \textbf{Libraries}{: Sklearn, NumPy, Pandas, Matplotlib, Tensorflow,} \\
    
 \end{itemize}



 %-----------Languages-----------
\section{Languages Known}
  \resumeSubHeadingListStart
    \resumeItem{Kannada, English, Hindi, Marathi}
    
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Assessments / Certifications}
  \resumeSubHeadingListStart
    \resumeItem{AI Foundation Certification - Infosys Springboard}
    \resumeItem{Supervised Machine Learning: Regression and Classification - Coursera}
    \resumeItem{Postman API Fundamentals- Postman}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}